---
title: "MyFirst rMarkdown Presentation"
author: "Olusanya Oluwole"
date: "4/16/2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## New Slides

New slides are created with heading preceded by 2 ## signs.

***

You can create a slide with a heading (title) with 3 *** asterisks signs.

## Title
2 ## signs for title

### Top Level Subtitle
3 ### for top level subtitle

#### Second Level Subtitle
4 ### for second level subtitle and so on.

## Make a List

Use bullets

- Bullet 1
- Bullet 2 etc.

Use numbering

1. Item 1
2. Item 2 etc.

## Formatting

Plain text

*Italicized text*

**Bold text**

`Syntax highlight` e.g; `for (i %in% 1 : 10)`

## Embelded R Code

```{r}
summary(mtcars)
```

## Remove Comment Characters "##" from Output
```{r, comment=""}
summary(mtcars)
```


## Show Code Used to Generate Output
```{r, comment="", echo=TRUE}
summary(mtcars)
```


## Show Code Used to Generate Output
This can also be achieved by get rid of default knitter option
```
knitr::opts_chunk$set(echo = FALSE)
```
## Show Codes without Output
```{r, comment="", eval=FALSE, echo=TRUE}
summary(mtcars)
```


## Example of a plot

```{r, fig.align='center', fig.cap="Plot showing Mile/gallon vs Weight", }
plot(mtcars$wt, mtcars$mpg, xlab = "Weight", ylab = "Mile/gallon")
```

